---
title: "Eye-tracking Analysis"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---

```{r libraries and import}
library(tidyverse)
library(emmeans)
library(afex)
library(ggpubr)
library(here)

data <- read.csv("SpiderPairedData.csv")

options(scipen = 999)
```

In the butterfly section, I included some comments of what each line does since the remaining chunks are formatted very similarly.

```{r butterfly}
# total dwell time dataframe which grabs the spider and non-spider columns for dwell time for a single question and makes two rows per subject (one of their dwell time for each photo in the pair)
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT2_Spider, DT2_Butterfly) %>% 
  pivot_longer(cols = c(DT2_Spider:DT2_Butterfly), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  # relabels the photo description in the image column
  mutate(image = fct_recode(image, "Q1_Spider" = "DT2_Spider",
                                   "Q1_Butterfly" = "DT2_Butterfly"),
         # makes sure that Spider would be left of Butterfly on a graph
         image = fct_relevel(image, "Q1_Spider", "Q1_Butterfly"),
         # makes sure Gender and PhobiaRank are factors
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

# same for first run dwell time
frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT2_Spider, FRDT2_Butterfly) %>% 
  pivot_longer(cols = c(FRDT2_Spider:FRDT2_Butterfly), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q1_Spider" = "FRDT2_Spider",
                                   "Q1_Butterfly" = "FRDT2_Butterfly"),
         image = fct_relevel(image, "Q1_Spider", "Q1_Butterfly"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

# same for first fixation time
fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT2_Spider, FFT2_Butterfly) %>% 
  pivot_longer(cols = c(FFT2_Spider:FFT2_Butterfly), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q1_Spider" = "FFT2_Spider",
                                   "Q1_Butterfly" = "FFT2_Butterfly"),
         image = fct_relevel(image, "Q1_Spider", "Q1_Butterfly"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

# same for run count
rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC2_Spider, RC2_Butterfly) %>% 
  pivot_longer(cols = c(RC2_Spider:RC2_Butterfly), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q1_Spider" = "RC2_Spider",
                                   "Q1_Butterfly" = "RC2_Butterfly"),
         image = fct_relevel(image, "Q1_Spider", "Q1_Butterfly"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

# since full_join only allows the joining of two dataframes
# join dwell time and first run dwell time
butterfly1 <- full_join(dt, frdt, 
                        by = c("Subject", "Gender", "PhobiaRank", "image"))
# join first fixation time and run count
butterfly2 <- full_join(fft, rc, 
                        by = c("Subject", "Gender", "PhobiaRank", "image"))
# join the two partial to have all four variables in a single frame
butterfly <- full_join(butterfly1, butterfly2, 
                       by = c("Subject", "Gender", "PhobiaRank", "image"))


# Three-way repeated measures ANOVA using the subject averages
dwell <- aov_ez(id = "Subject", # individual identifier
                dv = "dwell_time", # the dependent variable
                data = butterfly, # the dataframe
                within = "image", #the within-subjects variable 
                between = c("Gender", "PhobiaRank")) # the between-subjects variables
# get the results of the ANOVA test
summary(dwell)
# get the predictions from the model
Q1_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))
# Run a Tukey Honest Significant Differences (HSD) test on the significant interaction
emmeans(dwell, pairwise ~ image * Gender, adjust = "tukey")
# get the predictions from the model for the I x G interaction
Q1_ig_dt_predictions <- data.frame(question = "Q1", 
                           emmeans(dwell, ~ image:Gender)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Butterfly")) %>% 
  select(-lower.CL, -upper.CL)

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = butterfly,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q1_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = butterfly,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q1_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = butterfly,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q1_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r insect}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT5a_Spider, DT5a_Insect) %>% 
  pivot_longer(cols = c(DT5a_Spider:DT5a_Insect), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q2_Spider" = "DT5a_Spider",
                                   "Q2_Insect" = "DT5a_Insect"),
         image = fct_relevel(image, "Q2_Spider", "Q2_Insect"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT5a_Spider, FRDT5a_Insect) %>% 
  pivot_longer(cols = c(FRDT5a_Spider:FRDT5a_Insect), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q2_Spider" = "FRDT5a_Spider",
                                   "Q2_Insect" = "FRDT5a_Insect"),
         image = fct_relevel(image, "Q2_Spider", "Q2_Insect"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT5a_Spider, FFT5a_Insect) %>% 
  pivot_longer(cols = c(FFT5a_Spider:FFT5a_Insect), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q2_Spider" = "FFT5a_Spider",
                                   "Q2_Insect" = "FFT5a_Insect"),
         image = fct_relevel(image, "Q2_Spider", "Q2_Insect"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC5a_Spider, RC5a_Insect) %>% 
  pivot_longer(cols = c(RC5a_Spider:RC5a_Insect), 
              names_to = "image", 
              values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q2_Spider" = "RC5a_Spider",
                                   "Q2_Insect" = "RC5a_Insect"),
         image = fct_relevel(image, "Q2_Spider", "Q2_Insect"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

insect1 <- full_join(dt, frdt, 
                     by = c("Subject", "Gender", "PhobiaRank", "image"))
insect2 <- full_join(fft, rc, 
                     by = c("Subject", "Gender", "PhobiaRank", "image"))
insect <- full_join(insect1, insect2, 
                    by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = insect,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q2_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = insect,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q2_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = insect,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q2_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = insect,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q2_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r insect eyes}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT3b_6eyeSp, DT3b_2eyeIn) %>% 
  pivot_longer(cols = c(DT3b_6eyeSp:DT3b_2eyeIn), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q3_Spider" = "DT3b_6eyeSp",
                                   "Q3_Insect Eyes" = "DT3b_2eyeIn"),
         image = fct_relevel(image, "Q3_Spider", "Q3_Insect Eyes"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT3b_6eyeSp, FRDT3b_2eyeIn) %>% 
  pivot_longer(cols = c(FRDT3b_6eyeSp:FRDT3b_2eyeIn), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q3_Spider" = "FRDT3b_6eyeSp",
                                   "Q3_Insect Eyes" = "FRDT3b_2eyeIn"),
         image = fct_relevel(image, "Q3_Spider", "Q3_Insect Eyes"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT3b_6eyeSp, FFT3b_2eyeIn) %>% 
  pivot_longer(cols = c(FFT3b_6eyeSp:FFT3b_2eyeIn), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q3_Spider" = "FFT3b_6eyeSp",
                                   "Q3_Insect Eyes" = "FFT3b_2eyeIn"),
         image = fct_relevel(image, "Q3_Spider", "Q3_Insect Eyes"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC3b_6eyeSp, RC3b_2eyeIn) %>% 
  pivot_longer(cols = c(RC3b_6eyeSp:RC3b_2eyeIn), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q3_Spider" = "RC3b_6eyeSp",
                                   "Q3_Insect Eyes" = "RC3b_2eyeIn"),
         image = fct_relevel(image, "Q3_Spider", "Q3_Insect Eyes"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

insecteyes1 <- full_join(dt, frdt, 
                         by = c("Subject", "Gender", "PhobiaRank", "image"))
insecteyes2 <- full_join(fft, rc, 
                         by = c("Subject", "Gender", "PhobiaRank", "image"))
insecteyes <- full_join(insecteyes1, insecteyes2, 
                        by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = insecteyes,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q3_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = insecteyes,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q3_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = insecteyes,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q3_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = insecteyes,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q3_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r arachnid}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT5c_Spider, DT5c_NonArac) %>% 
  pivot_longer(cols = c(DT5c_Spider:DT5c_NonArac), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q4_Spider" = "DT5c_Spider",
                                   "Q4_Non-Spider Arachnid" = "DT5c_NonArac"),
         image = fct_relevel(image, "Q4_Spider", "Q4_Non-Spider Arachnid"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT5c_Spider, FRDT5c_NonArac) %>% 
  pivot_longer(cols = c(FRDT5c_Spider:FRDT5c_NonArac), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q4_Spider" = "FRDT5c_Spider",
                                   "Q4_Non-Spider Arachnid" = "FRDT5c_NonArac"),
         image = fct_relevel(image, "Q4_Spider", "Q4_Non-Spider Arachnid"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT5c_Spider, FFT5c_NonArac) %>% 
  pivot_longer(cols = c(FFT5c_Spider:FFT5c_NonArac), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q4_Spider" = "FFT5c_Spider",
                                   "Q4_Non-Spider Arachnid" = "FFT5c_NonArac"),
         image = fct_relevel(image, "Q4_Spider", "Q4_Non-Spider Arachnid"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC5c_Spider, RC5c_NonArac) %>% 
  pivot_longer(cols = c(RC5c_Spider:RC5c_NonArac), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q4_Spider" = "RC5c_Spider",
                                   "Q4_Non-Spider Arachnid" = "RC5c_NonArac"),
         image = fct_relevel(image, "Q4_Spider", "Q4_Non-Spider Arachnid"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

arachnid1 <- full_join(dt, frdt, 
                       by = c("Subject", "Gender", "PhobiaRank", "image"))
arachnid2 <- full_join(fft, rc, 
                       by = c("Subject", "Gender", "PhobiaRank", "image"))
arachnid <- full_join(arachnid1, arachnid2, 
                      by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = arachnid,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q4_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))
emmeans(dwell, pairwise ~ image * Gender, adjust = "tukey")
emmeans(dwell, pairwise ~ image * Gender * PhobiaRank, adjust = "tukey")
Q4_igp_dt_predictions <- data.frame(emmeans(dwell, ~ image:Gender:PhobiaRank)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_recode(photo, "Spider" = "Spider",
                            "Non-Spider Arachnid" = "Non.Spider.Arachnid"),
         photo = fct_relevel(photo, "Spider", "Non-Spider Arachnid")) %>% 
  select(-lower.CL, -upper.CL)

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = arachnid,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q4_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))
emmeans(first_dwell, pairwise ~ image * Gender * PhobiaRank, adjust = "tukey")
Q4_igp_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image:Gender:PhobiaRank)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_recode(photo, "Spider" = "Spider",
                            "Non-Spider Arachnid" = "Non.Spider.Arachnid"),
         photo = fct_relevel(photo, "Spider", "Non-Spider Arachnid")) %>% 
  select(-lower.CL, -upper.CL)

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = arachnid,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q4_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))
emmeans(first_fix, pairwise ~ image * Gender * PhobiaRank, adjust = "tukey")
Q4_igp_fft_predictions <- data.frame(emmeans(first_fix, ~ image:Gender:PhobiaRank)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_recode(photo, "Spider" = "Spider",
                            "Non-Spider Arachnid" = "Non.Spider.Arachnid"),
         photo = fct_relevel(photo, "Spider", "Non-Spider Arachnid")) %>% 
  select(-lower.CL, -upper.CL)

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = arachnid,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q4_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r myriapod}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT5b_Spider, DT5b_Myriapod) %>% 
  pivot_longer(cols = c(DT5b_Spider:DT5b_Myriapod), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q5_Spider" = "DT5b_Spider",
                                   "Q5_Myriapod" = "DT5b_Myriapod"),
         image = fct_relevel(image, "Q5_Spider", "Q5_Myriapod"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT5b_Spider, FRDT5b_Myriapod) %>% 
  pivot_longer(cols = c(FRDT5b_Spider:FRDT5b_Myriapod), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q5_Spider" = "FRDT5b_Spider",
                                   "Q5_Myriapod" = "FRDT5b_Myriapod"),
         image = fct_relevel(image, "Q5_Spider", "Q5_Myriapod"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT5b_Spider, FFT5b_Myriapod) %>% 
  pivot_longer(cols = c(FFT5b_Spider:FFT5b_Myriapod), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q5_Spider" = "FFT5b_Spider",
                                   "Q5_Myriapod" = "FFT5b_Myriapod"),
         image = fct_relevel(image, "Q5_Spider", "Q5_Myriapod"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC5b_Spider, RC5b_Myriapod) %>% 
  pivot_longer(cols = c(RC5b_Spider:RC5b_Myriapod), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q5_Spider" = "RC5b_Spider",
                                   "Q5_Myriapod" = "RC5b_Myriapod"),
         image = fct_relevel(image, "Q5_Spider", "Q5_Myriapod"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

myriapod1 <- full_join(dt, frdt, 
                       by = c("Subject", "Gender", "PhobiaRank", "image"))
myriapod2 <- full_join(fft, rc, 
                       by = c("Subject", "Gender", "PhobiaRank", "image"))
myriapod <- full_join(myriapod1, myriapod2, 
                      by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = myriapod,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q5_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = myriapod,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q5_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))
emmeans(first_dwell, pairwise ~ image * Gender, adjust = "tukey")
Q5_ig_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image:Gender)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Myriapod")) %>% 
  select(-lower.CL, -upper.CL)

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = myriapod,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q5_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = myriapod,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q5_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

I found a I x G x P interaction in dwell time that was not reported in the paper for scorpion, but the post hoc analysis reveals no significant differences.

```{r scorpion}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT11_NonScorp, DT11_Scorpion) %>% 
  pivot_longer(cols = c(DT11_NonScorp:DT11_Scorpion), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q6_Spider" = "DT11_NonScorp",
                                   "Q6_Scorpion" = "DT11_Scorpion"),
         image = fct_relevel(image, "Q6_Spider", "Q6_Scorpion"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT11_NonScorp, FRDT11_Scorpion) %>% 
  pivot_longer(cols = c(FRDT11_NonScorp:FRDT11_Scorpion), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q6_Spider" = "FRDT11_NonScorp",
                                   "Q6_Scorpion" = "FRDT11_Scorpion"),
         image = fct_relevel(image, "Q6_Spider", "Q6_Scorpion"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT11_Non.Scorp, FFT11_Scorpion) %>% 
  pivot_longer(cols = c(FFT11_Non.Scorp:FFT11_Scorpion), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q6_Spider" = "FFT11_Non.Scorp",
                                   "Q6_Scorpion" = "FFT11_Scorpion"),
         image = fct_relevel(image, "Q6_Spider", "Q6_Scorpion"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC11_NonScorp, RC11_Scorpion) %>% 
  pivot_longer(cols = c(RC11_NonScorp:RC11_Scorpion), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q6_Spider" = "RC11_NonScorp",
                                   "Q6_Scorpion" = "RC11_Scorpion"),
         image = fct_relevel(image, "Q6_Spider", "Q6_Scorpion"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

scorpion1 <- full_join(dt, frdt, 
                       by = c("Subject", "Gender", "PhobiaRank", "image"))
scorpion2 <- full_join(fft, rc, 
                       by = c("Subject", "Gender", "PhobiaRank", "image"))
scorpion <- full_join(scorpion1, scorpion2, 
                      by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = scorpion,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q6_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))
emmeans(dwell, pairwise ~ image * PhobiaRank, adjust = "tukey")
emmeans(dwell, pairwise ~ image * Gender * PhobiaRank, adjust = "tukey")
Q6_ip_dt_predictions <- data.frame(emmeans(dwell, ~ image:PhobiaRank)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Scorpion")) %>% 
  select(-lower.CL, -upper.CL)

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = scorpion,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q6_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))
emmeans(first_dwell, pairwise ~ image * Gender, adjust = "tukey")
Q6_ig_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image:Gender)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Scorpion")) %>% 
  select(-lower.CL, -upper.CL)
emmeans(first_dwell, pairwise ~ image * PhobiaRank, adjust = "tukey")
Q6_ip_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image:PhobiaRank)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Scorpion")) %>% 
  select(-lower.CL, -upper.CL)

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = scorpion,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q6_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))
emmeans(first_fix, pairwise ~ image * PhobiaRank, adjust = "tukey")
Q6_ip_fft_predictions <- data.frame(emmeans(first_fix, ~ image:PhobiaRank)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Scorpion")) %>% 
  select(-lower.CL, -upper.CL)

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = scorpion,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q6_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r eye size}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT3a_6PlusEyes, DT3a_JS) %>% 
  pivot_longer(cols = c(DT3a_6PlusEyes:DT3a_JS), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q7_Smaller Eyes" = "DT3a_6PlusEyes",
                                   "Q7_Enlarged Eyes" = "DT3a_JS"),
         image = fct_relevel(image, "Q7_Smaller Eyes", "Q7_Enlarged Eyes"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT3a_6PlusEyes, FRDT3a_JS) %>% 
  pivot_longer(cols = c(FRDT3a_6PlusEyes:FRDT3a_JS), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q7_Smaller Eyes" = "FRDT3a_6PlusEyes",
                                   "Q7_Enlarged Eyes" = "FRDT3a_JS"),
         image = fct_relevel(image, "Q7_Smaller Eyes", "Q7_Enlarged Eyes"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT3a_6PlusEyes, FFT3a_JS) %>% 
  pivot_longer(cols = c(FFT3a_6PlusEyes:FFT3a_JS), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q7_Smaller Eyes" = "FFT3a_6PlusEyes",
                                   "Q7_Enlarged Eyes" = "FFT3a_JS"),
         image = fct_relevel(image, "Q7_Smaller Eyes", "Q7_Enlarged Eyes"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC3a_6PlusEyes, RC3a_JS) %>% 
  pivot_longer(cols = c(RC3a_6PlusEyes:RC3a_JS), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q7_Smaller Eyes" = "RC3a_6PlusEyes",
                                   "Q7_Enlarged Eyes" = "RC3a_JS"),
         image = fct_relevel(image, "Q7_Smaller Eyes", "Q7_Enlarged Eyes"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

eyes_size1 <- full_join(dt, frdt, 
                        by = c("Subject", "Gender", "PhobiaRank", "image"))
eyes_size2 <- full_join(fft, rc, 
                        by = c("Subject", "Gender", "PhobiaRank", "image"))
eyes_size <- full_join(eyes_size1, eyes_size2, 
                       by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = eyes_size,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q7_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = eyes_size,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q7_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = eyes_size,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q7_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = eyes_size,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q7_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r color}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT4_JSNoCol, DT4_JSCol) %>% 
  pivot_longer(cols = c(DT4_JSNoCol:DT4_JSCol), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q8_Less color" = "DT4_JSNoCol",
                                   "Q8_More color" = "DT4_JSCol"),
         image = fct_relevel(image, "Q8_Less color", "Q8_More color"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT4_JSNoCol, FRDT4_JSCol) %>% 
  pivot_longer(cols = c(FRDT4_JSNoCol:FRDT4_JSCol), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q8_Less color" = "FRDT4_JSNoCol",
                                   "Q8_More color" = "FRDT4_JSCol"),
         image = fct_relevel(image, "Q8_Less color", "Q8_More color"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT4_JSNoCol, FFT4_JSCol) %>% 
  pivot_longer(cols = c(FFT4_JSNoCol:FFT4_JSCol), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q8_Less color" = "FFT4_JSNoCol",
                                   "Q8_More color" = "FFT4_JSCol"),
         image = fct_relevel(image, "Q8_Less color", "Q8_More color"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC4_JSNoCol, RC4_JSCol) %>% 
  pivot_longer(cols = c(RC4_JSNoCol:RC4_JSCol), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q8_Less color" = "RC4_JSNoCol",
                                   "Q8_More color" = "RC4_JSCol"),
         image = fct_relevel(image, "Q8_Less color", "Q8_More color"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

color1 <- full_join(dt, frdt, 
                    by = c("Subject", "Gender", "PhobiaRank", "image"))
color2 <- full_join(fft, rc, 
                    by = c("Subject", "Gender", "PhobiaRank", "image"))
color <- full_join(color1, color2, 
                   by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = color,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q8_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = color,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q8_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))
emmeans(first_dwell, pairwise ~ image * PhobiaRank, adjust = "tukey")
Q8_ip_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image:PhobiaRank)) %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_recode(photo, "More color" = "More.color",
                            "Less color" = "Less.color"),
         photo = fct_relevel(photo, "Less color", "More color")) %>% 
  select(-lower.CL, -upper.CL)

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = color,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q8_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = color,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q8_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r web}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT6_Ground, DT6_Web) %>% 
  pivot_longer(cols = c(DT6_Ground:DT6_Web), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q9_No web" = "DT6_Ground",
                                   "Q9_Web" = "DT6_Web"),
         image = fct_relevel(image, "Q9_No web", "Q9_Web"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT6_Ground, FRDT6_Web) %>% 
  pivot_longer(cols = c(FRDT6_Ground:FRDT6_Web), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q9_No web" = "FRDT6_Ground",
                                   "Q9_Web" = "FRDT6_Web"),
         image = fct_relevel(image, "Q9_No web", "Q9_Web"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT6_Ground, FFT6_Web) %>% 
  pivot_longer(cols = c(FFT6_Ground:FFT6_Web), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q9_No web" = "FFT6_Ground",
                                   "Q9_Web" = "FFT6_Web"),
         image = fct_relevel(image, "Q9_No web", "Q9_Web"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC6_Ground, RC6_Web) %>% 
  pivot_longer(cols = c(RC6_Ground:RC6_Web), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q9_No web" = "RC6_Ground",
                                   "Q9_Web" = "RC6_Web"),
         image = fct_relevel(image, "Q9_No web", "Q9_Web"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

web1 <- full_join(dt, frdt, 
                  by = c("Subject", "Gender", "PhobiaRank", "image"))
web2 <- full_join(fft, rc, 
                  by = c("Subject", "Gender", "PhobiaRank", "image"))
web <- full_join(web1, web2, 
                 by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = web,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q9_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = web,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q9_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = web,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q9_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = web,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q9_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r eggs}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT7_NoEggs, DT7_Eggs) %>% 
  pivot_longer(cols = c(DT7_NoEggs:DT7_Eggs), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q10_No eggs" = "DT7_NoEggs",
                                   "Q10_Eggs" = "DT7_Eggs"),
         image = fct_relevel(image, "Q10_No eggs", "Q10_Eggs"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT7_NoEggs, FRDT7_Eggs) %>% 
  pivot_longer(cols = c(FRDT7_NoEggs:FRDT7_Eggs), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q10_No eggs" = "FRDT7_NoEggs",
                                   "Q10_Eggs" = "FRDT7_Eggs"),
         image = fct_relevel(image, "Q10_No eggs", "Q10_Eggs"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT7_NoEggs, FFT7_Eggs) %>% 
  pivot_longer(cols = c(FFT7_NoEggs:FFT7_Eggs), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q10_No eggs" = "FFT7_NoEggs",
                                   "Q10_Eggs" = "FFT7_Eggs"),
         image = fct_relevel(image, "Q10_No eggs", "Q10_Eggs"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC7_NoEggs, RC7_Eggs) %>% 
  pivot_longer(cols = c(RC7_NoEggs:RC7_Eggs), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q10_No eggs" = "RC7_NoEggs",
                                   "Q10_Eggs" = "RC7_Eggs"),
         image = fct_relevel(image, "Q10_No eggs", "Q10_Eggs"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

eggs1 <- full_join(dt, frdt, 
                   by = c("Subject", "Gender", "PhobiaRank", "image"))
eggs2 <- full_join(fft, rc, 
                   by = c("Subject", "Gender", "PhobiaRank", "image"))
eggs <- full_join(eggs1, eggs2, 
                  by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = eggs,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q10_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = eggs,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q10_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = eggs,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q10_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = eggs,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q10_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r fangs}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT9_NoFangs, DT9_Fangs) %>% 
  pivot_longer(cols = c(DT9_NoFangs:DT9_Fangs), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q11_No fangs" = "DT9_NoFangs",
                                   "Q11_Fangs" = "DT9_Fangs"),
         image = fct_relevel(image, "Q11_No fangs", "Q11_Fangs"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT9_NoFangs, FRDT9_Fangs) %>% 
  pivot_longer(cols = c(FRDT9_NoFangs:FRDT9_Fangs), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q11_No fangs" = "FRDT9_NoFangs",
                                   "Q11_Fangs" = "FRDT9_Fangs"),
         image = fct_relevel(image, "Q11_No fangs", "Q11_Fangs"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT9_NoFangs, FFT9_Fangs) %>% 
  pivot_longer(cols = c(FFT9_NoFangs:FFT9_Fangs), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q11_No fangs" = "FFT9_NoFangs",
                                   "Q11_Fangs" = "FFT9_Fangs"),
         image = fct_relevel(image, "Q11_No fangs", "Q11_Fangs"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC9_NoFangs, RC9_Fangs) %>% 
  pivot_longer(cols = c(RC9_NoFangs:RC9_Fangs), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q11_No fangs" = "RC9_NoFangs",
                                   "Q11_Fangs" = "RC9_Fangs"),
         image = fct_relevel(image, "Q11_No fangs", "Q11_Fangs"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fangs1 <- full_join(dt, frdt, 
                    by = c("Subject", "Gender", "PhobiaRank", "image"))
fangs2 <- full_join(fft, rc, 
                    by = c("Subject", "Gender", "PhobiaRank", "image"))
fangs <- full_join(fangs1, fangs2, 
                   by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = fangs,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q11_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = fangs,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q11_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = fangs,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q11_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = fangs,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q11_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
emmeans(run_count, pairwise ~ image * Gender * PhobiaRank, adjust = "tukey")
```

```{r eating}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT8_NotEating, DT8_Eating) %>% 
  pivot_longer(cols = c(DT8_NotEating:DT8_Eating), names_to = "image", values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q12_Not eating" = "DT8_NotEating",
                                   "Q12_Eating" = "DT8_Eating"),
         image = fct_relevel(image, "Q12_Not eating", "Q12_Eating"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT8_NotEating, FRDT8_Eating) %>% 
  pivot_longer(cols = c(FRDT8_NotEating:FRDT8_Eating), names_to = "image", values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q12_Not eating" = "FRDT8_NotEating",
                                   "Q12_Eating" = "FRDT8_Eating"),
         image = fct_relevel(image, "Q12_Not eating", "Q12_Eating"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT8_NotEating, FFT8_Eating) %>% 
  pivot_longer(cols = c(FFT8_NotEating:FFT8_Eating), names_to = "image", values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q12_Not eating" = "FFT8_NotEating",
                                   "Q12_Eating" = "FFT8_Eating"),
         image = fct_relevel(image, "Q12_Not eating", "Q12_Eating"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC8_NotEating, RC8_Eating) %>% 
  pivot_longer(cols = c(RC8_NotEating:RC8_Eating), names_to = "image", values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q12_Not eating" = "RC8_NotEating",
                                   "Q12_Eating" = "RC8_Eating"),
         image = fct_relevel(image, "Q12_Not eating", "Q12_Eating"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

eating1 <- full_join(dt, frdt, by = c("Subject", "Gender", "PhobiaRank", "image"))
eating2 <- full_join(fft, rc, by = c("Subject", "Gender", "PhobiaRank", "image"))
eating <- full_join(eating1, eating2, by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = eating,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q12_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = eating,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q12_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = eating,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q12_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = eating,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q12_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

```{r hairy}
dt <- data %>% 
  select(Subject, Gender, PhobiaRank, DT10_NotHairy, DT10_Hairy) %>% 
  pivot_longer(cols = c(DT10_NotHairy:DT10_Hairy), 
               names_to = "image", 
               values_to = "dwell_time") %>% 
  mutate(image = fct_recode(image, "Q13_Not hairy" = "DT10_NotHairy",
                                   "Q13_Hairy" = "DT10_Hairy"),
         image = fct_relevel(image, "Q13_Not hairy", "Q13_Hairy"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

frdt <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT10_NotHairy, FRDT10_Hairy) %>% 
  pivot_longer(cols = c(FRDT10_NotHairy:FRDT10_Hairy), 
               names_to = "image", 
               values_to = "first_run_dwell_time") %>% 
  mutate(image = fct_recode(image, "Q13_Not hairy" = "FRDT10_NotHairy",
                                   "Q13_Hairy" = "FRDT10_Hairy"),
         image = fct_relevel(image, "Q13_Not hairy", "Q13_Hairy"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

fft <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT10_NotHairy, FFT10_Hairy) %>% 
  pivot_longer(cols = c(FFT10_NotHairy:FFT10_Hairy), 
               names_to = "image", 
               values_to = "first_fixation_time") %>% 
  mutate(image = fct_recode(image, "Q13_Not hairy" = "FFT10_NotHairy",
                                   "Q13_Hairy" = "FFT10_Hairy"),
         image = fct_relevel(image, "Q13_Not hairy", "Q13_Hairy"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

rc <- data %>% 
  select(Subject, Gender, PhobiaRank, RC10_NotHairy, RC10_Hairy) %>% 
  pivot_longer(cols = c(RC10_NotHairy:RC10_Hairy), 
               names_to = "image", 
               values_to = "run_count") %>% 
  mutate(image = fct_recode(image, "Q13_Not hairy" = "RC10_NotHairy",
                                   "Q13_Hairy" = "RC10_Hairy"),
         image = fct_relevel(image, "Q13_Not hairy", "Q13_Hairy"),
         Gender = factor(Gender),
         PhobiaRank = factor(PhobiaRank))

hairy1 <- full_join(dt, frdt, 
                    by = c("Subject", "Gender", "PhobiaRank", "image"))
hairy2 <- full_join(fft, rc, 
                    by = c("Subject", "Gender", "PhobiaRank", "image"))
hairy <- full_join(hairy1, hairy2, 
                   by = c("Subject", "Gender", "PhobiaRank", "image"))

dwell <- aov_ez(id = "Subject",
                dv = "dwell_time",
                data = hairy,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(dwell)
Q13_image_dt_predictions <- data.frame(emmeans(dwell, ~ image))

first_dwell <- aov_ez(id = "Subject",
                dv = "first_run_dwell_time",
                data = hairy,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_dwell)
Q13_image_frdt_predictions <- data.frame(emmeans(first_dwell, ~ image))

first_fix <- aov_ez(id = "Subject",
                dv = "first_fixation_time",
                data = hairy,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(first_fix)
Q13_image_fft_predictions <- data.frame(emmeans(first_fix, ~ image))

run_count <- aov_ez(id = "Subject",
                dv = "run_count",
                data = hairy,
                within = "image",
                between = c("Gender", "PhobiaRank"))
summary(run_count)
Q13_image_rc_predictions <- data.frame(emmeans(run_count, ~ image))
```

This is where I prepare the data for graphing.

```{r wrangle for graphs}
# dwell time, spider vs non-spider
# binds the predictions calculated in earlier chunks
dt_predictions_SpiderVsNonSpider <- rbind(Q1_image_dt_predictions, 
                                          Q2_image_dt_predictions, 
                                          Q3_image_dt_predictions, 
                                          Q4_image_dt_predictions, 
                                          Q5_image_dt_predictions, 
                                          Q6_image_dt_predictions) 
# fixes the labels as they will appear on the graph
dt_predictions_SpiderVsNonSpider$photo <- factor(dt_predictions_SpiderVsNonSpider$image,
                        levels = c("Q1_Spider", "Q1_Butterfly", 
                                   "Q2_Spider", "Q2_Insect", 
                                   "Q3_Spider", "Q3_Insect.Eyes", 
                                   "Q4_Spider", "Q4_Non.Spider.Arachnid", 
                                   "Q5_Spider", "Q5_Myriapod", 
                                   "Q6_Spider", "Q6_Scorpion"),
                        labels = c("Spider", "Butterfly", 
                                   "Spider", "Insect", 
                                   "Spider", "Insect Eyes", 
                                   "Spider", "Non-Spider Arachnid", 
                                   "Spider", "Myriapod", 
                                   "Spider", "Scorpion"))
dt_predictions_SpiderVsNonSpider <- dt_predictions_SpiderVsNonSpider %>% 
# creats a new label for the type of image so we can use it to color the graph
  mutate(spider_yn = ifelse(photo == "Spider", "Spider", "Non-Spider"),
         spider_yn = fct_relevel(spider_yn, "Spider", "Non-Spider")) %>% 
# creates a question column to make the groups in the graph
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
# cleans up with only the columns of interest
  select(question, photo, spider_yn, emmean, SE, df)


dt_raw_SpiderVsNonSpider <- data %>% 
# selects only the dwell time of the first 6 questions
  select(Subject, Gender, PhobiaRank, DT2_Spider, DT2_Butterfly, DT5a_Spider, DT5a_Insect,
                        DT3b_6eyeSp, DT3b_2eyeIn, DT5c_Spider, DT5c_NonArac,
                        DT5b_Spider, DT5b_Myriapod, DT11_NonScorp, DT11_Scorpion) %>% 
  pivot_longer(cols = c(DT2_Spider:DT11_Scorpion), values_to = "dwell_time", names_to = "image") %>% 
# replace labels to match the associated predictions frame
  mutate(image = fct_recode(image, "Q1_Spider" = "DT2_Spider",
                                   "Q1_Butterfly" = "DT2_Butterfly",
                                   "Q2_Spider" = "DT5a_Spider",
                                   "Q2_Insect" = "DT5a_Insect",
                                   "Q3_Spider" = "DT3b_6eyeSp",
                                   "Q3_Insect.Eyes" = "DT3b_2eyeIn",
                                   "Q4_Spider" = "DT5c_Spider",
                                   "Q4_Non.Spider.Arachnid" = "DT5c_NonArac",
                                   "Q5_Spider" = "DT5b_Spider",
                                   "Q5_Myriapod" = "DT5b_Myriapod",
                                   "Q6_Spider" = "DT11_NonScorp",
                                   "Q6_Scorpion" = "DT11_Scorpion"))
# fixes the labels as they will appear on the graph
dt_raw_SpiderVsNonSpider$photo <- factor(dt_raw_SpiderVsNonSpider$image,
                        levels = c("Q1_Spider", "Q1_Butterfly", 
                                   "Q2_Spider", "Q2_Insect", 
                                   "Q3_Spider", "Q3_Insect.Eyes", 
                                   "Q4_Spider", "Q4_Non.Spider.Arachnid", 
                                   "Q5_Spider", "Q5_Myriapod", 
                                   "Q6_Spider", "Q6_Scorpion"),
                        labels = c("Spider", "Butterfly", 
                                   "Spider", "Insect", 
                                   "Spider", "Insect Eyes", 
                                   "Spider", "Non-Spider Arachnid", 
                                   "Spider", "Myriapod", 
                                   "Spider", "Scorpion"))
dt_raw_SpiderVsNonSpider <- dt_raw_SpiderVsNonSpider %>% 
# creats a new label for the type of image so we can use it to color the graph
  mutate(spider_yn = ifelse(photo == "Spider", "Spider", "Non-Spider"),
         spider_yn = fct_relevel(spider_yn, "Spider", "Non-Spider")) %>% 
# creates a question column to make the groups in the graph
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
# cleans up with only the columns of interest
  select(Subject, Gender, PhobiaRank, question, photo, spider_yn, dwell_time)


# dwell time, with and without features
dt_predictions_features <- rbind(Q7_image_dt_predictions, 
                                 Q8_image_dt_predictions, 
                                 Q9_image_dt_predictions, 
                                 Q10_image_dt_predictions, 
                                 Q11_image_dt_predictions, 
                                 Q12_image_dt_predictions,
                                 Q13_image_dt_predictions) 
dt_predictions_features$photo <- factor(dt_predictions_features$image,
                        levels = c("Q7_Smaller.Eyes", "Q7_Enlarged.Eyes", 
                                   "Q8_Less.color", "Q8_More.color", 
                                   "Q9_No.web", "Q9_Web", 
                                   "Q10_No.eggs", "Q10_Eggs", 
                                   "Q11_No.fangs", "Q11_Fangs", 
                                   "Q12_Not.eating", "Q12_Eating",
                                   "Q13_Not.hairy", "Q13_Hairy"),
                        labels = c("Smaller Eyes", "Enlarged Eyes", 
                                   "Less Color", "More Color", 
                                   "No Web", "Web", 
                                   "No Eggs", "Eggs",
                                   "No Fangs", "Fangs", 
                                   "Not Eating", "Eating", 
                                   "Not Hairy", "Hairy"))
dt_predictions_features <- dt_predictions_features %>% 
  mutate(feature_yn = ifelse(photo == "Smaller Eyes"| photo == "Less Color" | photo == "No Web" | photo == "No Eggs" | photo == "No Fangs" | photo == "Not Eating" | photo == "Not Hairy", "Without Feature", "With Feature"),
         feature_yn = fct_relevel(feature_yn, "Without Feature", "With Feature")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(question, photo, feature_yn, emmean, SE, df)

dt_raw_features <- data %>% 
  select(Subject, Gender, PhobiaRank, DT3a_6PlusEyes, DT3a_JS, DT4_JSNoCol, DT4_JSCol,
         DT6_Ground, DT6_Web, DT7_NoEggs, DT7_Eggs, DT9_NoFangs, DT9_Fangs, DT8_NotEating,
         DT8_Eating, DT10_NotHairy, DT10_Hairy) %>% 
  pivot_longer(cols = c(DT3a_6PlusEyes:DT10_Hairy), values_to = "dwell_time", names_to = "image") %>% 
  mutate(image = fct_recode(image, "Q7_Smaller Eyes" = "DT3a_6PlusEyes",
                                   "Q7_Enlarged Eyes" = "DT3a_JS",
                                   "Q8_Less color" = "DT4_JSNoCol",
                                   "Q8_More color" = "DT4_JSCol",
                                   "Q9_No web" = "DT6_Ground",
                                   "Q9_Web" = "DT6_Web",
                                   "Q10_No eggs" = "DT7_NoEggs",
                                   "Q10_Eggs" = "DT7_Eggs",
                                   "Q11_No fangs" = "DT9_NoFangs",
                                   "Q11_Fangs" = "DT9_Fangs",
                                   "Q12_Not eating" = "DT8_NotEating",
                                   "Q12_Eating" = "DT8_Eating",
                                   "Q13_Not hairy" = "DT10_NotHairy",
                                   "Q13_Hairy" = "DT10_Hairy")) 
dt_raw_features$photo <- factor(dt_raw_features$image,
                        levels = c("Q7_Smaller Eyes", "Q7_Enlarged Eyes", 
                                   "Q8_Less color", "Q8_More color", 
                                   "Q9_No web", "Q9_Web", 
                                   "Q10_No eggs", "Q10_Eggs", 
                                   "Q11_No fangs", "Q11_Fangs", 
                                   "Q12_Not eating", "Q12_Eating",
                                   "Q13_Not hairy", "Q13_Hairy"),
                        labels = c("Smaller Eyes", "Enlarged Eyes", 
                                   "Less Color", "More Color", 
                                   "No Web", "Web", 
                                   "No Eggs", "Eggs",
                                   "No Fangs", "Fangs", 
                                   "Not Eating", "Eating", 
                                   "Not Hairy", "Hairy"))
dt_raw_features <- dt_raw_features %>% 
  mutate(feature_yn = ifelse(photo == "Smaller Eyes"| photo == "Less Color" | photo == "No Web" | photo == "No Eggs" | photo == "No Fangs" | photo == "Not Eating" | photo == "Not Hairy", "Without Feature", "With Feature"),
         feature_yn = fct_relevel(feature_yn, "Without Feature", "With Feature")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(Subject, Gender, PhobiaRank, question, photo, feature_yn, dwell_time)

# first run dwell time, spider vs non-spider
frdt_predictions_SpiderVsNonSpider <- rbind(Q1_image_frdt_predictions, 
                                          Q2_image_frdt_predictions, 
                                          Q3_image_frdt_predictions, 
                                          Q4_image_frdt_predictions, 
                                          Q5_image_frdt_predictions, 
                                          Q6_image_frdt_predictions) 
frdt_predictions_SpiderVsNonSpider$photo <- factor(frdt_predictions_SpiderVsNonSpider$image,
                        levels = c("Q1_Spider", "Q1_Butterfly", 
                                   "Q2_Spider", "Q2_Insect", 
                                   "Q3_Spider", "Q3_Insect.Eyes", 
                                   "Q4_Spider", "Q4_Non.Spider.Arachnid", 
                                   "Q5_Spider", "Q5_Myriapod", 
                                   "Q6_Spider", "Q6_Scorpion"),
                        labels = c("Spider", "Butterfly", 
                                   "Spider", "Insect", 
                                   "Spider", "Insect Eyes", 
                                   "Spider", "Non-Spider Arachnid", 
                                   "Spider", "Myriapod", 
                                   "Spider", "Scorpion"))
frdt_predictions_SpiderVsNonSpider <- frdt_predictions_SpiderVsNonSpider %>% 
  mutate(spider_yn = ifelse(photo == "Spider", "Spider", "Non-Spider"),
         spider_yn = fct_relevel(spider_yn, "Spider", "Non-Spider")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(question, photo, spider_yn, emmean, SE, df)

frdt_raw_SpiderVsNonSpider <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT2_Spider, FRDT2_Butterfly, FRDT5a_Spider, FRDT5a_Insect,
                        FRDT3b_6eyeSp, FRDT3b_2eyeIn, FRDT5c_Spider, FRDT5c_NonArac,
                        FRDT5b_Spider, FRDT5b_Myriapod, FRDT11_NonScorp, FRDT11_Scorpion) %>% 
  pivot_longer(cols = c(FRDT2_Spider:FRDT11_Scorpion), values_to = "first_run_dwell_time", names_to = "image") %>% 
  mutate(image = fct_recode(image, "Q1_Spider" = "FRDT2_Spider",
                                   "Q1_Butterfly" = "FRDT2_Butterfly",
                                   "Q2_Spider" = "FRDT5a_Spider",
                                   "Q2_Insect" = "FRDT5a_Insect",
                                   "Q3_Spider" = "FRDT3b_6eyeSp",
                                   "Q3_Insect.Eyes" = "FRDT3b_2eyeIn",
                                   "Q4_Spider" = "FRDT5c_Spider",
                                   "Q4_Non-Spider Arachnid" = "FRDT5c_NonArac",
                                   "Q5_Spider" = "FRDT5b_Spider",
                                   "Q5_Myriapod" = "FRDT5b_Myriapod",
                                   "Q6_Spider" = "FRDT11_NonScorp",
                                   "Q6_Scorpion" = "FRDT11_Scorpion")) 
frdt_raw_SpiderVsNonSpider$photo <- factor(frdt_raw_SpiderVsNonSpider$image,
                        levels = c("Q1_Spider", "Q1_Butterfly", 
                                   "Q2_Spider", "Q2_Insect", 
                                   "Q3_Spider", "Q3_Insect.Eyes", 
                                   "Q4_Spider", "Q4_Non-Spider Arachnid", 
                                   "Q5_Spider", "Q5_Myriapod", 
                                   "Q6_Spider", "Q6_Scorpion"),
                        labels = c("Spider", "Butterfly", 
                                   "Spider", "Insect", 
                                   "Spider", "Insect Eyes", 
                                   "Spider", "Non-Spider Arachnid", 
                                   "Spider", "Myriapod", 
                                   "Spider", "Scorpion"))
frdt_raw_SpiderVsNonSpider <- frdt_raw_SpiderVsNonSpider %>% 
  mutate(spider_yn = ifelse(photo == "Spider", "Spider", "Non-Spider"),
         spider_yn = fct_relevel(spider_yn, "Spider", "Non-Spider")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(Subject, Gender, PhobiaRank, question, photo, spider_yn, first_run_dwell_time)

# first run dwell time, with and without features
frdt_predictions_features <- rbind(Q7_image_frdt_predictions, 
                                 Q8_image_frdt_predictions, 
                                 Q9_image_frdt_predictions, 
                                 Q10_image_frdt_predictions, 
                                 Q11_image_frdt_predictions, 
                                 Q12_image_frdt_predictions,
                                 Q13_image_frdt_predictions) 
frdt_predictions_features$photo <- factor(frdt_predictions_features$image,
                        levels = c("Q7_Smaller.Eyes", "Q7_Enlarged.Eyes", 
                                   "Q8_Less.color", "Q8_More.color", 
                                   "Q9_No.web", "Q9_Web", 
                                   "Q10_No.eggs", "Q10_Eggs", 
                                   "Q11_No.fangs", "Q11_Fangs", 
                                   "Q12_Not.eating", "Q12_Eating",
                                   "Q13_Not.hairy", "Q13_Hairy"),
                        labels = c("Smaller Eyes", "Enlarged Eyes", 
                                   "Less Color", "More Color", 
                                   "No Web", "Web", 
                                   "No Eggs", "Eggs",
                                   "No Fangs", "Fangs", 
                                   "Not Eating", "Eating", 
                                   "Not Hairy", "Hairy"))
frdt_predictions_features <- frdt_predictions_features %>% 
  mutate(feature_yn = ifelse(photo == "Smaller Eyes"| photo == "Less Color" | photo == "No Web" | photo == "No Eggs" | photo == "No Fangs" | photo == "Not Eating" | photo == "Not Hairy", "Without Feature", "With Feature"),
         feature_yn = fct_relevel(feature_yn, "Without Feature", "With Feature")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(question, photo, feature_yn, emmean, SE, df)

frdt_raw_features <- data %>% 
  select(Subject, Gender, PhobiaRank, FRDT3a_6PlusEyes, FRDT3a_JS, FRDT4_JSNoCol, FRDT4_JSCol,
         FRDT6_Ground, FRDT6_Web, FRDT7_NoEggs, FRDT7_Eggs, FRDT9_NoFangs, FRDT9_Fangs, FRDT8_NotEating,
         FRDT8_Eating, FRDT10_NotHairy, FRDT10_Hairy) %>% 
  pivot_longer(cols = c(FRDT3a_6PlusEyes:FRDT10_Hairy), values_to = "first_run_dwell_time", names_to = "image") %>% 
  mutate(image = fct_recode(image, "Q7_Smaller Eyes" = "FRDT3a_6PlusEyes",
                                   "Q7_Enlarged Eyes" = "FRDT3a_JS",
                                   "Q8_Less color" = "FRDT4_JSNoCol",
                                   "Q8_More color" = "FRDT4_JSCol",
                                   "Q9_No web" = "FRDT6_Ground",
                                   "Q9_Web" = "FRDT6_Web",
                                   "Q10_No eggs" = "FRDT7_NoEggs",
                                   "Q10_Eggs" = "FRDT7_Eggs",
                                   "Q11_No fangs" = "FRDT9_NoFangs",
                                   "Q11_Fangs" = "FRDT9_Fangs",
                                   "Q12_Not eating" = "FRDT8_NotEating",
                                   "Q12_Eating" = "FRDT8_Eating",
                                   "Q13_Not hairy" = "FRDT10_NotHairy",
                                   "Q13_Hairy" = "FRDT10_Hairy")) 
frdt_raw_features$photo <- factor(frdt_raw_features$image,
                        levels = c("Q7_Smaller Eyes", "Q7_Enlarged Eyes", 
                                   "Q8_Less color", "Q8_More color", 
                                   "Q9_No web", "Q9_Web", 
                                   "Q10_No eggs", "Q10_Eggs", 
                                   "Q11_No fangs", "Q11_Fangs", 
                                   "Q12_Not eating", "Q12_Eating",
                                   "Q13_Not hairy", "Q13_Hairy"),
                        labels = c("Smaller Eyes", "Enlarged Eyes", 
                                   "Less Color", "More Color", 
                                   "No Web", "Web", 
                                   "No Eggs", "Eggs",
                                   "No Fangs", "Fangs", 
                                   "Not Eating", "Eating", 
                                   "Not Hairy", "Hairy"))
frdt_raw_features <- frdt_raw_features %>% 
  mutate(feature_yn = ifelse(photo == "Smaller Eyes"| photo == "Less Color" | photo == "No Web" | photo == "No Eggs" | photo == "No Fangs" | photo == "Not Eating" | photo == "Not Hairy", "Without Feature", "With Feature"),
         feature_yn = fct_relevel(feature_yn, "Without Feature", "With Feature")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(Subject, Gender, PhobiaRank, question, photo, feature_yn, first_run_dwell_time)

# first fixation time, spider vs non-spider
fft_predictions_SpiderVsNonSpider <- rbind(Q1_image_fft_predictions, 
                                          Q2_image_fft_predictions, 
                                          Q3_image_fft_predictions, 
                                          Q4_image_fft_predictions, 
                                          Q5_image_fft_predictions, 
                                          Q6_image_fft_predictions) 
fft_predictions_SpiderVsNonSpider$photo <- factor(fft_predictions_SpiderVsNonSpider$image,
                        levels = c("Q1_Spider", "Q1_Butterfly", 
                                   "Q2_Spider", "Q2_Insect", 
                                   "Q3_Spider", "Q3_Insect.Eyes", 
                                   "Q4_Spider", "Q4_Non.Spider.Arachnid", 
                                   "Q5_Spider", "Q5_Myriapod", 
                                   "Q6_Spider", "Q6_Scorpion"),
                        labels = c("Spider", "Butterfly", 
                                   "Spider", "Insect", 
                                   "Spider", "Insect Eyes", 
                                   "Spider", "Non-Spider Arachnid", 
                                   "Spider", "Myriapod", 
                                   "Spider", "Scorpion"))
fft_predictions_SpiderVsNonSpider <- fft_predictions_SpiderVsNonSpider %>% 
  mutate(spider_yn = ifelse(photo == "Spider", "Spider", "Non-Spider"),
         spider_yn = fct_relevel(spider_yn, "Spider", "Non-Spider")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(question, photo, spider_yn, emmean, SE, df)

fft_raw_SpiderVsNonSpider <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT2_Spider, FFT2_Butterfly, FFT5a_Spider, FFT5a_Insect,
                        FFT3b_6eyeSp, FFT3b_2eyeIn, FFT5c_Spider, FFT5c_NonArac,
                        FFT5b_Spider, FFT5b_Myriapod, FFT11_Non.Scorp, FFT11_Scorpion) %>% 
  pivot_longer(cols = c(FFT2_Spider:FFT11_Scorpion), values_to = "first_fixation_time", names_to = "image") %>% 
  mutate(image = fct_recode(image, "Q1_Spider" = "FFT2_Spider",
                                   "Q1_Butterfly" = "FFT2_Butterfly",
                                   "Q2_Spider" = "FFT5a_Spider",
                                   "Q2_Insect" = "FFT5a_Insect",
                                   "Q3_Spider" = "FFT3b_6eyeSp",
                                   "Q3_Insect.Eyes" = "FFT3b_2eyeIn",
                                   "Q4_Spider" = "FFT5c_Spider",
                                   "Q4_Non.Spider.Arachnid" = "FFT5c_NonArac",
                                   "Q5_Spider" = "FFT5b_Spider",
                                   "Q5_Myriapod" = "FFT5b_Myriapod",
                                   "Q6_Spider" = "FFT11_Non.Scorp",
                                   "Q6_Scorpion" = "FFT11_Scorpion")) 
fft_raw_SpiderVsNonSpider$photo <- factor(fft_raw_SpiderVsNonSpider$image,
                        levels = c("Q1_Spider", "Q1_Butterfly", 
                                   "Q2_Spider", "Q2_Insect", 
                                   "Q3_Spider", "Q3_Insect.Eyes", 
                                   "Q4_Spider", "Q4_Non.Spider.Arachnid", 
                                   "Q5_Spider", "Q5_Myriapod", 
                                   "Q6_Spider", "Q6_Scorpion"),
                        labels = c("Spider", "Butterfly", 
                                   "Spider", "Insect", 
                                   "Spider", "Insect Eyes", 
                                   "Spider", "Non-Spider Arachnid", 
                                   "Spider", "Myriapod", 
                                   "Spider", "Scorpion"))
fft_raw_SpiderVsNonSpider <- fft_raw_SpiderVsNonSpider %>% 
  mutate(spider_yn = ifelse(photo == "Spider", "Spider", "Non-Spider"),
         spider_yn = fct_relevel(spider_yn, "Spider", "Non-Spider")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(Subject, Gender, PhobiaRank, question, photo, spider_yn, first_fixation_time)

# first fixation time, with and without features
fft_predictions_features <- rbind(Q7_image_fft_predictions, 
                                 Q8_image_fft_predictions, 
                                 Q9_image_fft_predictions, 
                                 Q10_image_fft_predictions, 
                                 Q11_image_fft_predictions, 
                                 Q12_image_fft_predictions,
                                 Q13_image_fft_predictions)
fft_predictions_features$photo <- factor(fft_predictions_features$image,
                        levels = c("Q7_Smaller.Eyes", "Q7_Enlarged.Eyes", 
                                   "Q8_Less.color", "Q8_More.color", 
                                   "Q9_No.web", "Q9_Web", 
                                   "Q10_No.eggs", "Q10_Eggs", 
                                   "Q11_No.fangs", "Q11_Fangs", 
                                   "Q12_Not.eating", "Q12_Eating",
                                   "Q13_Not.hairy", "Q13_Hairy"),
                        labels = c("Smaller Eyes", "Enlarged Eyes", 
                                   "Less Color", "More Color", 
                                   "No Web", "Web", 
                                   "No Eggs", "Eggs",
                                   "No Fangs", "Fangs", 
                                   "Not Eating", "Eating", 
                                   "Not Hairy", "Hairy"))
fft_predictions_features <- fft_predictions_features %>% 
  mutate(feature_yn = ifelse(photo == "Smaller Eyes"| photo == "Less Color" | photo == "No Web" | photo == "No Eggs" | photo == "No Fangs" | photo == "Not Eating" | photo == "Not Hairy", "Without Feature", "With Feature"),
         feature_yn = fct_relevel(feature_yn, "Without Feature", "With Feature")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(question, photo, feature_yn, emmean, SE, df)

fft_raw_features <- data %>% 
  select(Subject, Gender, PhobiaRank, FFT3a_6PlusEyes, FFT3a_JS, FFT4_JSNoCol, FFT4_JSCol,
         FFT6_Ground, FFT6_Web, FFT7_NoEggs, FFT7_Eggs, FFT9_NoFangs, FFT9_Fangs, FFT8_NotEating,
         FFT8_Eating, FFT10_NotHairy, FFT10_Hairy) %>% 
  pivot_longer(cols = c(FFT3a_6PlusEyes:FFT10_Hairy), values_to = "first_fixation_time", names_to = "image") %>% 
  mutate(image = fct_recode(image, "Q7_Smaller Eyes" = "FFT3a_6PlusEyes",
                                   "Q7_Enlarged Eyes" = "FFT3a_JS",
                                   "Q8_Less color" = "FFT4_JSNoCol",
                                   "Q8_More color" = "FFT4_JSCol",
                                   "Q9_No web" = "FFT6_Ground",
                                   "Q9_Web" = "FFT6_Web",
                                   "Q10_No eggs" = "FFT7_NoEggs",
                                   "Q10_Eggs" = "FFT7_Eggs",
                                   "Q11_No fangs" = "FFT9_NoFangs",
                                   "Q11_Fangs" = "FFT9_Fangs",
                                   "Q12_Not eating" = "FFT8_NotEating",
                                   "Q12_Eating" = "FFT8_Eating",
                                   "Q13_Not hairy" = "FFT10_NotHairy",
                                   "Q13_Hairy" = "FFT10_Hairy")) 
fft_raw_features$photo <- factor(fft_raw_features$image,
                        levels = c("Q7_Smaller Eyes", "Q7_Enlarged Eyes", 
                                   "Q8_Less color", "Q8_More color", 
                                   "Q9_No web", "Q9_Web", 
                                   "Q10_No eggs", "Q10_Eggs", 
                                   "Q11_No fangs", "Q11_Fangs", 
                                   "Q12_Not eating", "Q12_Eating",
                                   "Q13_Not hairy", "Q13_Hairy"),
                        labels = c("Smaller Eyes", "Enlarged Eyes", 
                                   "Less Color", "More Color", 
                                   "No Web", "Web", 
                                   "No Eggs", "Eggs",
                                   "No Fangs", "Fangs", 
                                   "Not Eating", "Eating", 
                                   "Not Hairy", "Hairy"))
fft_raw_features <- fft_raw_features %>% 
  mutate(feature_yn = ifelse(photo == "Smaller Eyes"| photo == "Less Color" | photo == "No Web" | photo == "No Eggs" | photo == "No Fangs" | photo == "Not Eating" | photo == "Not Hairy", "Without Feature", "With Feature"),
         feature_yn = fct_relevel(feature_yn, "Without Feature", "With Feature")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(Subject, Gender, PhobiaRank, question, photo, feature_yn, first_fixation_time)

# run count, spider vs non-spider
rc_predictions_SpiderVsNonSpider <- rbind(Q1_image_rc_predictions, 
                                          Q2_image_rc_predictions, 
                                          Q3_image_rc_predictions, 
                                          Q4_image_rc_predictions, 
                                          Q5_image_rc_predictions, 
                                          Q6_image_rc_predictions) 
rc_predictions_SpiderVsNonSpider$photo <- factor(rc_predictions_SpiderVsNonSpider$image,
                        levels = c("Q1_Spider", "Q1_Butterfly", 
                                   "Q2_Spider", "Q2_Insect", 
                                   "Q3_Spider", "Q3_Insect.Eyes", 
                                   "Q4_Spider", "Q4_Non.Spider.Arachnid", 
                                   "Q5_Spider", "Q5_Myriapod", 
                                   "Q6_Spider", "Q6_Scorpion"),
                        labels = c("Spider", "Butterfly", 
                                   "Spider", "Insect", 
                                   "Spider", "Insect Eyes", 
                                   "Spider", "Non-Spider Arachnid", 
                                   "Spider", "Myriapod", 
                                   "Spider", "Scorpion"))
rc_predictions_SpiderVsNonSpider <- rc_predictions_SpiderVsNonSpider %>% 
  mutate(spider_yn = ifelse(photo == "Spider", "Spider", "Non-Spider"),
         spider_yn = fct_relevel(spider_yn, "Spider", "Non-Spider")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(question, photo, spider_yn, emmean, SE, df)

rc_raw_SpiderVsNonSpider <- data %>% 
  select(Subject, Gender, PhobiaRank, RC2_Spider, RC2_Butterfly, RC5a_Spider, RC5a_Insect,
                        RC3b_6eyeSp, RC3b_2eyeIn, RC5c_Spider, RC5c_NonArac,
                        RC5b_Spider, RC5b_Myriapod, RC11_NonScorp, RC11_Scorpion) %>% 
  pivot_longer(cols = c(RC2_Spider:RC11_Scorpion), values_to = "run_count", names_to = "image") %>% 
  mutate(image = fct_recode(image, "Q1_Spider" = "RC2_Spider",
                                   "Q1_Butterfly" = "RC2_Butterfly",
                                   "Q2_Spider" = "RC5a_Spider",
                                   "Q2_Insect" = "RC5a_Insect",
                                   "Q3_Spider" = "RC3b_6eyeSp",
                                   "Q3_Insect.Eyes" = "RC3b_2eyeIn",
                                   "Q4_Spider" = "RC5c_Spider",
                                   "Q4_Non.Spider.Arachnid" = "RC5c_NonArac",
                                   "Q5_Spider" = "RC5b_Spider",
                                   "Q5_Myriapod" = "RC5b_Myriapod",
                                   "Q6_Spider" = "RC11_NonScorp",
                                   "Q6_Scorpion" = "RC11_Scorpion")) 
rc_raw_SpiderVsNonSpider$photo <- factor(rc_raw_SpiderVsNonSpider$image,
                        levels = c("Q1_Spider", "Q1_Butterfly", 
                                   "Q2_Spider", "Q2_Insect", 
                                   "Q3_Spider", "Q3_Insect.Eyes", 
                                   "Q4_Spider", "Q4_Non.Spider.Arachnid", 
                                   "Q5_Spider", "Q5_Myriapod", 
                                   "Q6_Spider", "Q6_Scorpion"),
                        labels = c("Spider", "Butterfly", 
                                   "Spider", "Insect", 
                                   "Spider", "Insect Eyes", 
                                   "Spider", "Non-Spider Arachnid", 
                                   "Spider", "Myriapod", 
                                   "Spider", "Scorpion"))
rc_raw_SpiderVsNonSpider <- rc_raw_SpiderVsNonSpider %>% 
  mutate(spider_yn = ifelse(photo == "Spider", "Spider", "Non-Spider"),
         spider_yn = fct_relevel(spider_yn, "Spider", "Non-Spider")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(Subject, Gender, PhobiaRank, question, photo, spider_yn, run_count)

# run count, with and without features
rc_predictions_features <- rbind(Q7_image_rc_predictions, 
                                 Q8_image_rc_predictions, 
                                 Q9_image_rc_predictions, 
                                 Q10_image_rc_predictions, 
                                 Q11_image_rc_predictions, 
                                 Q12_image_rc_predictions,
                                 Q13_image_rc_predictions) 
rc_predictions_features$photo <- factor(rc_predictions_features$image,
                        levels = c("Q7_Smaller.Eyes", "Q7_Enlarged.Eyes", 
                                   "Q8_Less.color", "Q8_More.color", 
                                   "Q9_No.web", "Q9_Web", 
                                   "Q10_No.eggs", "Q10_Eggs", 
                                   "Q11_No.fangs", "Q11_Fangs", 
                                   "Q12_Not.eating", "Q12_Eating",
                                   "Q13_Not.hairy", "Q13_Hairy"),
                        labels = c("Smaller Eyes", "Enlarged Eyes", 
                                   "Less Color", "More Color", 
                                   "No Web", "Web", 
                                   "No Eggs", "Eggs",
                                   "No Fangs", "Fangs", 
                                   "Not Eating", "Eating", 
                                   "Not Hairy", "Hairy"))
rc_predictions_features <- rc_predictions_features %>% 
  mutate(feature_yn = ifelse(photo == "Smaller Eyes"| photo == "Less Color" | photo == "No Web" | photo == "No Eggs" | photo == "No Fangs" | photo == "Not Eating" | photo == "Not Hairy", "Without Feature", "With Feature"),
         feature_yn = fct_relevel(feature_yn, "Without Feature", "With Feature")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(question, photo, feature_yn, emmean, SE, df)

rc_raw_features <- data %>% 
  select(Subject, Gender, PhobiaRank, RC3a_6PlusEyes, RC3a_JS, RC4_JSNoCol, RC4_JSCol,
         RC6_Ground, RC6_Web, RC7_NoEggs, RC7_Eggs, RC9_NoFangs, RC9_Fangs, RC8_NotEating,
         RC8_Eating, RC10_NotHairy, RC10_Hairy) %>% 
  pivot_longer(cols = c(RC3a_6PlusEyes:RC10_Hairy), values_to = "run_count", names_to = "image") %>% 
  mutate(image = fct_recode(image, "Q7_Smaller Eyes" = "RC3a_6PlusEyes",
                                   "Q7_Enlarged Eyes" = "RC3a_JS",
                                   "Q8_Less color" = "RC4_JSNoCol",
                                   "Q8_More color" = "RC4_JSCol",
                                   "Q9_No web" = "RC6_Ground",
                                   "Q9_Web" = "RC6_Web",
                                   "Q10_No eggs" = "RC7_NoEggs",
                                   "Q10_Eggs" = "RC7_Eggs",
                                   "Q11_No fangs" = "RC9_NoFangs",
                                   "Q11_Fangs" = "RC9_Fangs",
                                   "Q12_Not eating" = "RC8_NotEating",
                                   "Q12_Eating" = "RC8_Eating",
                                   "Q13_Not hairy" = "RC10_NotHairy",
                                   "Q13_Hairy" = "RC10_Hairy"))
rc_raw_features$photo <- factor(rc_raw_features$image,
                        levels = c("Q7_Smaller Eyes", "Q7_Enlarged Eyes", 
                                   "Q8_Less color", "Q8_More color", 
                                   "Q9_No web", "Q9_Web", 
                                   "Q10_No eggs", "Q10_Eggs", 
                                   "Q11_No fangs", "Q11_Fangs", 
                                   "Q12_Not eating", "Q12_Eating",
                                   "Q13_Not hairy", "Q13_Hairy"),
                        labels = c("Smaller Eyes", "Enlarged Eyes", 
                                   "Less Color", "More Color", 
                                   "No Web", "Web", 
                                   "No Eggs", "Eggs",
                                   "No Fangs", "Fangs", 
                                   "Not Eating", "Eating", 
                                   "Not Hairy", "Hairy"))
rc_raw_features <- rc_raw_features %>% 
  mutate(feature_yn = ifelse(photo == "Smaller Eyes"| photo == "Less Color" | photo == "No Web" | photo == "No Eggs" | photo == "No Fangs" | photo == "Not Eating" | photo == "Not Hairy", "Without Feature", "With Feature"),
         feature_yn = fct_relevel(feature_yn, "Without Feature", "With Feature")) %>% 
  separate(image, c("question", "other"), remove = FALSE, sep = "_") %>% 
  select(Subject, Gender, PhobiaRank, question, photo, feature_yn, run_count)

# wrangling for other figures
arachnid <- arachnid %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Non-Spider Arachnid"))

butterfly <- butterfly %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Butterfly"))

myriapod <- myriapod %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Myriapod"))

scorpion <- scorpion %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Spider", "Scorpion"))

color <- color %>% 
  separate(image, c("question", "photo"), sep = "_") %>% 
  mutate(photo = fct_relevel(photo, "Less color", "More color"))

```

For Emma: Let's make some graphs - woohoo!! Just make sure you run all of the lines above before graphing and checkout how the dataframes are set up.

```{r figure of image differences}
# this is the figure with 8 panels we talked about: one for each of the four variables and splitting the questions into spider/non-spider and with/without feature

# 1. Add code for ggplot of spider vs non-spider dwell time here
# raw: dt_raw_SpiderVsNonSpider (jittered points)
# predictions: dt_predictions_SpiderVsNonSpider (point and errorbars = emmean +/- SE)

dt_spider <- ggplot() +
# each layer here adds a new element to the graph
  geom_jitter(aes(x = photo, y = dwell_time, color = spider_yn), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = dt_raw_SpiderVsNonSpider) +
  geom_point(aes(x = photo, y = emmean, color = spider_yn), # the predicted mean
             size = 1.5,
             data = dt_predictions_SpiderVsNonSpider) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = spider_yn), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = dt_predictions_SpiderVsNonSpider) +
# this layer creates the spacing between each question on the graph
  facet_wrap(~question, strip.position = "bottom", scales = "free_x", 
             nrow = 1, ncol = 6) +
# the rest of the layers edit the appearance of the graph
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.text.x = element_blank()) # removes the labels created by facet_wrap
  

# 2. Add code for ggplot of with and without features dwell time here
# raw: dt_raw_features (jittered points)
# predictions: dt_predictions_features (point and errorbars = emmean +/- SE)
dt_feature <- ggplot() +
  geom_jitter(aes(x = photo, y = dwell_time, color = feature_yn), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = dt_raw_features) +
  geom_point(aes(x = photo, y = emmean, color = feature_yn), # the predicted mean
             size = 1.5,
             data = dt_predictions_features) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = feature_yn), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = dt_predictions_features) +
  facet_wrap(~question, strip.position = "bottom", scales = "free_x", 
             nrow = 1, ncol = 7) +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.text.x = element_blank()) # removes the labels created by facet_wrap

# 3. Add code for ggplot of spider vs non-spider first run dwell time here
# raw: frdt_raw_SpiderVsNonSpider (jittered points)
# predictions: frdt_predictions_SpiderVsNonSpider (point and errorbars = emmean +/- SE)
frdt_spider <- ggplot() +
  geom_jitter(aes(x = photo, y = first_run_dwell_time, color = spider_yn), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = frdt_raw_SpiderVsNonSpider) +
  geom_point(aes(x = photo, y = emmean, color = spider_yn), # the predicted mean
             size = 1.5,
             data = frdt_predictions_SpiderVsNonSpider) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = spider_yn), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = frdt_predictions_SpiderVsNonSpider) +
# this layer creates the spacing between each question on the graph
  facet_wrap(~question, strip.position = "bottom", scales = "free_x", 
             nrow = 1, ncol = 6) +
# the rest of the layers edit the appearance of the graph
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Run Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.text.x = element_blank()) # removes the labels created by facet_wrap

# 4. Add code for ggplot of with and without features first run dwell time here
# raw: frdt_raw_features (jittered points)
# predictions: frdt_predictions_features (point and errorbars = emmean +/- SE)
frdt_feature <- ggplot() +
  geom_jitter(aes(x = photo, y = first_run_dwell_time, color = feature_yn), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = frdt_raw_features) +
  geom_point(aes(x = photo, y = emmean, color = feature_yn), # the predicted mean
             size = 1.5,
             data = frdt_predictions_features) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = feature_yn), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = frdt_predictions_features) +
  facet_wrap(~question, strip.position = "bottom", scales = "free_x", 
             nrow = 1, ncol = 7) +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Run Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.text.x = element_blank()) # removes the labels created by facet_wrap

# 5. Add code for ggplot of spider vs non-spider first fixation time here
# raw: fft_raw_SpiderVsNonSpider (jittered points)
# predictions: fft_predictions_SpiderVsNonSpider (point and errorbars = emmean +/- SE)
fft_spider <- ggplot() +
  geom_jitter(aes(x = photo, y = first_fixation_time, color = spider_yn), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = fft_raw_SpiderVsNonSpider) +
  geom_point(aes(x = photo, y = emmean, color = spider_yn), # the predicted mean
             size = 1.5,
             data = fft_predictions_SpiderVsNonSpider) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = spider_yn), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = fft_predictions_SpiderVsNonSpider) +
# this layer creates the spacing between each question on the graph
  facet_wrap(~question, strip.position = "bottom", scales = "free_x", 
             nrow = 1, ncol = 6) +
# the rest of the layers edit the appearance of the graph
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Fixation Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.text.x = element_blank()) # removes the labels created by facet_wrap

# 6. Add code for ggplot of with and without features first fixation time here
# raw: fft_raw_features (jittered points)
# predictions: fft_predictions_features (point and errorbars = emmean +/- SE)
fft_feature <- ggplot() +
  geom_jitter(aes(x = photo, y = first_fixation_time, color = feature_yn), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = fft_raw_features) +
  geom_point(aes(x = photo, y = emmean, color = feature_yn), # the predicted mean
             size = 1.5,
             data = fft_predictions_features) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = feature_yn), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = fft_predictions_features) +
  facet_wrap(~question, strip.position = "bottom", scales = "free_x", 
             nrow = 1, ncol = 7) +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Fixation Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.text.x = element_blank()) # removes the labels created by facet_wrap

# 7. Add code for ggplot of spider vs non-spider run count here
# raw: rc_raw_SpiderVsNonSpider (jittered points)
# predictions: rc_predictions_SpiderVsNonSpider (point and errorbars = emmean +/- SE)
rc_spider <- ggplot() +
  geom_jitter(aes(x = photo, y = run_count, color = spider_yn), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = rc_raw_SpiderVsNonSpider) +
  geom_point(aes(x = photo, y = emmean, color = spider_yn), # the predicted mean
             size = 1.5,
             data = rc_predictions_SpiderVsNonSpider) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = spider_yn), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = rc_predictions_SpiderVsNonSpider) +
# this layer creates the spacing between each question on the graph
  facet_wrap(~question, strip.position = "bottom", scales = "free_x", 
             nrow = 1, ncol = 6) +
# the rest of the layers edit the appearance of the graph
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("Run Count") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.text.x = element_blank()) # removes the labels created by facet_wrap

# 8. Add code for ggplot of with and without features run count here
# raw: rc_raw_features (jittered points)
# predictions: rc_predictions_features (point and errorbars = emmean +/- SE)
rc_feature <- ggplot() +
  geom_jitter(aes(x = photo, y = run_count, color = feature_yn), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = rc_raw_features) +
  geom_point(aes(x = photo, y = emmean, color = feature_yn), # the predicted mean
             size = 1.5,
             data = rc_predictions_features) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = feature_yn), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = rc_predictions_features) +
  facet_wrap(~question, strip.position = "bottom", scales = "free_x", 
             nrow = 1, ncol = 7) +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("Run Count") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.text.x = element_blank()) # removes the labels created by facet_wrap

ggarrange(dt_spider, frdt_spider, fft_spider, rc_spider, 
          dt_feature, frdt_feature, fft_feature, rc_feature,
          nrow = 2,
          ncol = 4)
ggsave(here("image_diffs.png"), width = 8, height = 6, scale = 2)
```

```{r figure of spider vs non-spider arachnid}
# this is the figure about spider vs non-spider arachnids that had a bunch of three way interactions (there wasn't a three-way interaction for run count so I left that out)

# dwell time
# predictions: Q4_igp_dt_predictions
# raw data: arachnid
dt_arachnid <- ggplot() +
  geom_jitter(aes(x = photo, y = dwell_time, color = Gender), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = arachnid) +
  geom_point(aes(x = photo, y = emmean, color = Gender), # the predicted mean
             size = 1.5,
             data = Q4_igp_dt_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = Gender), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q4_igp_dt_predictions) +
  facet_wrap(~factor(PhobiaRank, c("Low", "Medium", "High")), strip.position = "bottom", scales = "free_x") +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  labs(y = "Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.background = element_rect(color = "#FFFFFF"))

# first run dwell time
# predictions: Q4_igp_frdt_predictions
# raw data: arachnid
frdt_arachnid <- ggplot() +
  geom_jitter(aes(x = photo, y = first_run_dwell_time, color = Gender), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = arachnid) +
  geom_point(aes(x = photo, y = emmean, color = Gender), # the predicted mean
             size = 1.5,
             data = Q4_igp_frdt_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = Gender), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q4_igp_frdt_predictions) +
  facet_wrap(~factor(PhobiaRank, c("Low", "Medium", "High")), strip.position = "bottom", scales = "free_x") +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Run Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.background = element_rect(color = "#FFFFFF"))

# first fixation time
# predictions: Q4_igp_fft_predictions
# raw data: arachnid
fft_arachnid <- ggplot() +
  geom_jitter(aes(x = photo, y = first_fixation_time, color = Gender), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = arachnid) +
  geom_point(aes(x = photo, y = emmean, color = Gender), # the predicted mean
             size = 1.5,
             data = Q4_igp_fft_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = Gender), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q4_igp_fft_predictions) +
  facet_wrap(~factor(PhobiaRank, c("Low", "Medium", "High")), strip.position = "bottom", scales = "free_x") +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Fixation Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12),
        strip.background = element_rect(color = "#FFFFFF"))


ggarrange(dt_arachnid, frdt_arachnid, fft_arachnid,
          nrow = 1, common.legend = TRUE, legend="top")
ggsave(here("spider_vs_arachnid.png"), width = 8, height = 5, scale = 1)
```

```{r figure of gender differences, echo=TRUE}
# this is the figure showing all of the graphs for image x gender interactions

# spider vs butterfly, dwell time
# predictions: Q1_ig_dt_predictions
# raw data: butterfly
gender_butterfly <- ggplot() +
  geom_jitter(aes(x = photo, y = dwell_time, color = Gender), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = butterfly) +
  geom_point(aes(x = photo, y = emmean, color = Gender), # the predicted mean
             size = 1.5,
             data = Q1_ig_dt_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = Gender), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q1_ig_dt_predictions) +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12))

# spider vs myriapod, first run dwell time
# predictions: Q5_ig_frdt_predictions
# raw data: myriapod
gender_myriapod <- ggplot() +
  geom_jitter(aes(x = photo, y = first_run_dwell_time, color = Gender), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = myriapod) +
  geom_point(aes(x = photo, y = emmean, color = Gender), # the predicted mean
             size = 1.5,
             data = Q5_ig_frdt_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = Gender), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q5_ig_frdt_predictions) +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Run Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12))

# scorpion vs non-scorpion, first run dwell time
# predictions: Q6_ig_frdt_predictions
# raw data: scorpion
gender_scorpion <- ggplot() +
  geom_jitter(aes(x = photo, y = first_run_dwell_time, color = Gender), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = scorpion) +
  geom_point(aes(x = photo, y = emmean, color = Gender), # the predicted mean
             size = 1.5,
             data = Q6_ig_frdt_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = Gender), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q6_ig_frdt_predictions) +
  scale_color_manual("", values = c("#d95f02", "#7570b3")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Run Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12))

ggarrange(gender_butterfly, gender_myriapod, gender_scorpion,
          nrow = 1, common.legend = TRUE, legend="top")
ggsave(here("imagexgender.png"), width = 8, height = 5, scale = 1)
```

```{r figure of phobia differences}
# this is the figure showing all of the graphs for image x PhobiaRank interactions

# scorpion vs non-scorpion, dwell time
# predictions: Q6_ip_dt_predictions
# raw data: scorpion
phobia_order <- c("Low", "Medium", "High")

scorpion <- scorpion %>% 
  mutate(PhobiaRank = factor(PhobiaRank),
         PhobiaRank = fct_relevel(PhobiaRank, "Low", "Medium", "High"))
Q6_ip_dt_predictions <- Q6_ip_dt_predictions %>% 
  mutate(PhobiaRank = factor(PhobiaRank),
         PhobiaRank = fct_relevel(PhobiaRank, "Low", "Medium", "High"))

phobia_scorpion_dt <- ggplot() +
  geom_jitter(aes(x = photo, y = dwell_time, color = PhobiaRank), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = scorpion) +
  geom_point(aes(x = photo, y = emmean, color = PhobiaRank), # the predicted mean
             size = 1.5,
             data = Q6_ip_dt_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = PhobiaRank), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q6_ip_dt_predictions) +
  #scale_x_discrete(limits = phobia_order) +
  scale_color_manual(values = c("#d95f02", "#7570b3", "#02a649")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12))


# scorpion vs non-scorpion, first run dwell time
# predictions: Q6_ip_frdt_predictions
# raw data: scorpion
phobia_scorpion_frdt <- ggplot() +
  geom_jitter(aes(x = photo, y = first_run_dwell_time, color = PhobiaRank), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = scorpion) +
  geom_point(aes(x = photo, y = emmean, color = PhobiaRank), # the predicted mean
             size = 1.5,
             data = Q6_ip_frdt_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = PhobiaRank), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q6_ip_frdt_predictions) +
  #scale_x_discrete(limits = phobia_order) +
  scale_color_manual("", values = c("#d95f02", "#7570b3", "#02a649")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Run Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12))


# scorpion vs non-scorpion, first fixation time
# predictions: Q6_ip_fft_predictions
# raw data: scorpion
phobia_scorpion_fft <- ggplot() +
  geom_jitter(aes(x = photo, y = first_fixation_time, color = PhobiaRank), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = scorpion) +
  geom_point(aes(x = photo, y = emmean, color = PhobiaRank), # the predicted mean
             size = 1.5,
             data = Q6_ip_fft_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = PhobiaRank), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q6_ip_fft_predictions) +
  #scale_x_discrete(limits = phobia_order) +
  scale_color_manual("", values = c("#d95f02", "#7570b3", "#02a649")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Fixation Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12))
  

# more color vs less color jumping spider, first run dwell time
# predictions: Q8_ip_frdt_predictions
# raw data: color
phobia_colorful_frdt <- ggplot() +
  geom_jitter(aes(x = photo, y = first_run_dwell_time, color = PhobiaRank), # the raw data layer
              alpha = 0.1, width = 0.25, size = 1,
              data = color) +
  geom_point(aes(x = photo, y = emmean, color = PhobiaRank), # the predicted mean
             size = 1.5,
             data = Q8_ip_frdt_predictions) +
  geom_errorbar(aes(x = photo, ymax = emmean + SE, ymin = emmean - SE, 
                    color = PhobiaRank), # the predicted standard error 
                width = 0.5, linewidth = 0.75,
                data = Q8_ip_frdt_predictions) +
  #scale_x_discrete(limits = phobia_order) +
  scale_color_manual("", values = c("#d95f02", "#7570b3", "#02a649")) + # set colors
  xlab("") + # x axis label, I left it blank
  ylab("First Run Dwell Time (ms)") + # y axis label
  theme_classic() + # removes the default background/gridlines
  theme(legend.position = "top", # moves legend to the top
        axis.text.x = element_text(angle = 45, vjust = 1, hjust=1, # rotates x-axis text
                                   color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 10), # sets font size/color
        axis.title.y = element_text(color = "black", size = 12))

ggarrange(phobia_scorpion_dt, phobia_scorpion_frdt, phobia_scorpion_fft, phobia_colorful_frdt,
          nrow = 1, ncolumn = 4, common.legend = TRUE, legend="top")
ggsave(here("imagexphobia.png"), width = 8, height = 6, scale = 1)
```
